Computer Science House Constitution

### 2024-09-17 constitution.tex
prevent multiple simultaneous memberships
Allow off floor intro members to sign packets

\asubsubsection{The Introductory Packet}
Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active Members who have passed a Membership Eval, all On-Floor Intro and Active Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
At the discretion of the Evals Director or as the result of an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.

>>>>

\asubsubsection{The Introductory Packet}
Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active and Intro Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
At the discretion of the Evals Director or as the result of an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.
